\section{Introduction}
\label{sec:introduction}
%Die technische Welt befindet sich in einem ständigen Wandel. Eine der gewichtigsten Neuerungen ist die Künstliche Intelligenz, oder kurz KI genannt.
%Künstliche Intelligenz ist der Grundbaustein diverser Grossunternehmen, wie beispielsweise Google oder Facebook.
%Auch bei den Privatpersonen hat die KI Einzug gehalten.
%Fei-Fei Li, Professor of Computer Science at Stanford University sagte mal:
% 	Zitat
The technical world is in a constant state of change. One of the most important innovations is artificial intelligence, or AI for short.
Artificial intelligence is the basic building block of various large companies, such as Google or Facebook.
AI has also found its way into the world of private individuals.
Fei-Fei Li, Professor of Computer Science at Stanford University said once:
\begin{quote}
	"I imagine a world in which AI is going to make us work more productively, live longer, and have cleaner energy."\cite{quotes_future}
\end{quote}
This scenario has already started. As an example of what artificial intelligence is capable of, the above paragraph was translated from a German text using the artificial intelligence of DeepL. The result is impressive.
However, AI is very versatile. In medicine, it is used to diagnose, cars should be able to drive independently or banks can recognize unauthorized use of credit cards \cite{artificial_intelligence_a_modern_approach}.
AI is used in nearly every industry and has become an important business factor.

Another challenge in today's world is the increasing data volume. More and more data should be processed in the shortest possible time. This makes fast hardware indispensable.

Project 5, AI High-Performance Solution on FPGA, covers the two topics artificial intelligence and fast data processing.
An eye-catcher for trade fairs is to be developed, where artificial intelligence is implemented on a field-programmable gate array (FPGA).
The eye-catcher is a throwing booth, which is able to detect throws and recognize certain objects in standalone operation.
It will be shown at exhibitions and represents the \textit{Fachhochschule Nordwestschweiz} (FHNW).

An Ultra96-V2 Development Board serves as hardware.
The used multiprocessor system-on-chip (MPSoC) --- an UltraScale+ MPSoC ZU3EG --- features an ARM-based microprocessors and an FPGA.

%The first step is to create the basic conditions for designing an AI.
The first step is to lay the foundations for designing an AI.
%This is, on the one hand, the throwing booth and, on the other hand, a dataset.
Those are the design and construction of the throwing booth and the collection of a sufficiently large dataset.
The dataset is necessary to train an artificial neural network (ANN).
In addition, project 5 includes a short introduction to artificial intelligence and machine learning.
%During the thesis, based on project 5, artificial intelligence will be implemented on the Ultra96 board.
During the thesis the required convolutional neural network will be trained and implemented on the Ultra96 board.

This technical report describes the theoretical and technical basis necessary for the realization of the project.
