\subsubsection{Image Change Detection}
\label{subsubsec:image_change_detection}
\todo[inline]{Citations, vspace before listings}

% The implementation of the difference computation and the average among all the pixels is described here
% Diff and Mean are done for every frame except the first one (FID = 0)
% Comparison done after the threshold averaging (see chapter threshold)

This section describes the implementation of the image change detection.
The difference computation and the averaging among all the pixels is done for every frame except the first one ($\texttt{FID} \geq 1$).
The threshold comparison and the throw detection is done for every frame after the threshold has been determined (see section \ref{subsubsec:threshold}).

% --------------------------------
\paragraph{Difference Computation}
The absolute difference pixel matrix $D$ can be calculated using equation \ref{eq:abs_diff}.
The implementation uses the OpenCV function \texttt{cv::absdiff} to calculate the per-element absolute difference between the two pixel matrices and saves it into \texttt{cv\_abs}, as shown in appendix \ref{app:throw_detection} on line \ref{lst:ln:abs_diff}.
% https://docs.opencv.org/4.1.1/d2/de8/group__core__array.html#ga6fef31bc8c4071cbc114a758a2b79c14

\begin{equation}
  D = |I_\text{FID} - I_\text{FID-1}| \quad\quad \text{with} \quad\quad \text{FID} \geq 1
  \label{eq:abs_diff}
\end{equation}

\begin{tabular}{rl}
  $D =$ & absolute difference pixel matrix \\
  $I =$ & image pixel matrix \\
\end{tabular}

% --------------------------------------
\paragraph{Average among all the pixels}
The mean absolute difference $\overline{\text{MD}}$ can be calculated using equation \ref{eq:mean_diff}.
The implementation uses the OpenCV function \texttt{cv::sum} to return the sum of array elements for each channel independently, as shown in appendix \ref{app:throw_detection} on line \ref{lst:ln:mean_diff}.
Since the Baumer \texttt{BayerRG8} pixel format consists of only one channel, the zeroth element is used.
% https://docs.opencv.org/4.1.1/d2/de8/group__core__array.html#ga716e10a2dd9e228e4d3c95818f106722

\begin{equation}
  \overline{\text{MD}} = \frac{1}{w\cdot h} \cdot \sum\limits_{i=1}^h \sum\limits_{j=1}^w D_{i,j}
  \label{eq:mean_diff}
\end{equation}

\begin{tabular}{rl}
  $\text{MD} =$ & mean absolute difference \\
  $D =$ & absolute difference pixel matrix \\
  $w =$ & width of the image in px \\
  $h =$ & height of the image in px \\
\end{tabular}

% --------------------------------------------------
\paragraph{Threshold Comparison and Throw Detection}
Listing \ref{lst:throw_detection} shows the implementaion of the threshold comparison and the throw detection.
Due to the specific implementation, it is possible to detect a single frame change.
This means that the image changes between two consecutive frames and then stays the way it is (e.g. sudden change of the ambient light).
Such a glitch is not a valid throw and shall therefore be ignored (see line \ref{lst:ln:glitch_removal}).
Figure \ref{subfig:algorithm_example_1} shows that a valid throw of an object would create at least two changes between individual frames.
The first one by entering and the second one by leaving the frame.
\vspace{5pt}
\begin{lstlisting}[style=C++, caption={Throw detection and glitch removal}, label=lst:throw_detection]
  if (mean_diff >= threshold) {
      if (!throw_bgn) {
        throw_bgn_idx = frame_id;
        throw_bgn = true;
      }
  } else {
    if (throw_bgn) {
      throw_end_idx = frame_id;

      // Remove glitches (single frame changes)
      if ((throw_end_idx - throw_bgn_idx) == 1) {(*\label{lst:ln:glitch_removal}*)
        throw_bgn = false;
      } else {
        throw_end = true;
      }
    }
  }
\end{lstlisting}

As long as no throw is detected, the current Baumer \texttt{Buffer} object is released after each processed frame (see listing \ref{lst:buffer_release}).
Whenever a glitch is removed, the size of the Baumer image buffer (\texttt{BS}) is reduced by one.
This is due to the fact that no reference to past \texttt{Buffer} objects is kept.
Such a reference is necessary to release the respective buffer entry.
It would be easy to solve this by keeping track of at least one past \texttt{Buffer} object.
However, this is not necessary, provided that the buffer size is large enough.
\vspace{5pt}
% BUG: Should not be released directly but with a delay of one!
\begin{lstlisting}[style=C++, caption={Release of the filled Baumer \texttt{Buffer} object}, label=lst:buffer_release]
  if (!throw_bgn) {
    pBufferFilled->QueueBuffer();
  }
\end{lstlisting}





% The implementation of the difference computation and the average among all the pixels is shown in listing \ref{lst:diff_computation_average}.

% \begin{lstlisting}[style=C++, caption={Difference computation and average among all the pixels}, label=lst:diff_computation_average]
%   cv::absdiff(cv_buffer[frame_id % buff_size], cv_buffer[(frame_id - 1) % buff_size], cv_abs);(*\label{lst:ln:abs_diff}*)
%   mean_diff = cv::sum(cv_abs)[0] / (width * height);(*\label{lst:ln:mean_diff}*)
% \end{lstlisting}
